Police Shootings and Racism in America

### 2020-10-16 submissionii.Rmd
data manipulated kinda

```{r load-data}
all <- read.csv("data/allshootingsdata.csv")
census <- read.csv("data/2013census.csv")[,-c(8,9)]
gun_provisions <- read.csv("data/gun_provisions.csv") %>% 
  filter(year == 2013)
```

>>>>

```{r load-data}
# Shootings
all <- read.csv("data/allshootingsdata.csv")
all <- all %>% 
  mutate(id = paste0("C", row_number()))

# Census Predictors
census <- read.csv("data/2013census.csv")[,-c(8,9)]
states <- lapply(census$department, function(x) str_extract_all(x,"\\([^()]+\\)")[[1]])
states <- substring(states, 2, nchar(states)-1)
census$state <- states

# Gun Law Predictors
gun_provisions <- read.csv("data/gun_provisions.csv") %>% 
  filter(year == 2013)
gun_provisions <- gun_provisions %>% 
  mutate(total_pr = rowSums(gun_provisions[,3:136]),
         deesc_train = ifelse(state %in% c("California", "New Mexico", "Texas", "Oklahoma", "South Dakota", "Illinois", "Indiana", "Tennessee", "Washington", "Missouri", "Georgia", "Ohio", "Maryland", "Massachusetts", "Connecticut", "Maine"), 1, 0)) %>% 
  select(state, total_pr, deesc_train)
gun_provisions$state <- state.abb[match(gun_provisions$state,state.name)]
```
